Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-10 W13report.tex
Changed help email adddress, rearranged authorship carriage returns to fill page L->R.

\author{
Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
Steve Groom (IPAC), Mario Juric (LSSTC),\\ 
Jeff Kantor (LSSTC),Ron Lambert (NOAO), Kian-Tat Lim (SLAC),\\
Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
and Daniel Wang (SLAC)\\ 
{\it for LSST Data Management}
\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\today}

@@

Please address any questions about this document to LSST-data@lsstcorp.org.

>>>>

\author{
Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
Steve Groom (IPAC), Mario Juric (LSSTC),Jeff Kantor (LSSTC),\\
Ron Lambert (NOAO), Kian-Tat Lim (SLAC),Bruce Mather (NCSA), \\
Serge Monkewitz (IPAC),Knut Olsen (NOAO), Steve Pietrowicz (NCSA), \\
Ray Plante (NCSA),Dick Shaw (NOAO), Douglas Smith (SLAC), \\
Schuyler Van Dyk (IPAC), and Daniel Wang (SLAC)\\ 
{\it for LSST Data Management}
\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\today}

@@

Please address any questions about this document to dm-help@lsstcorp.org.
